---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# Star Wars lorem ipsum generator

Using [ForcemJS](https://github.com/scottyg/ForcemJS), this package produces Star Wars filler text.

```r
if(!(require(devtools))) install.package("devtools")
devtools::install_github("MangoTheCat/swli")
```

## How it works - reference wrappers
```{r}
library(swli)
aNewHope(paragraphs = 1)
theEmpireStrikesBack(paragraphs = 1)
returnOfTheJedi(paragraphs = 1)
places(paragraphs = 1)
people(paragraphs = 1)
```

## How it works - root function
```{r}
library(swli)
# Change paragraphs
swli(paragraphs = 2)
# Change type of return
swli(type = "e4")
# Get an item from each type
options <- c("e4", "e5", "e6", "places", "people")
mapply(swli,  type = options,  paragraphs = 1)
```

## Quirks & Bugs
Due to the randomisation of paragraphs for return, the original JS auther returns 5 paragraphs when a request for length 0 comes in.

The `window` scope in the original javascript errors when called by V8 so the version locally has this replaced with `global`.