---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  cache.extra = knitr::rand_seed
)
options(width = 72)
```

# Star Wars lorem ipsum generator

Using [ForcemJS](https://github.com/scottyg/ForcemJS), this package
produces Star Wars filler text.

```r
if (!(require(devtools))) install.packages("devtools")
devtools::install_github("MangoTheCat/swli")
```

## How it works — reference wrappers

```{r}
library(swli)
strwrap(aNewHope(paragraphs = 1))
strwrap(theEmpireStrikesBack(paragraphs = 1))
strwrap(returnOfTheJedi(paragraphs = 1))
places(paragraphs = 1)
people(paragraphs = 1)
```

## How it works — root function

```{r}
library(swli)
```

## Change paragraphs

```{r}
strwrap(swli(paragraphs = 2))
```

## Change type of return

```{r}
strwrap(swli(type = "e4"))
```

## Get an item from each type

```{r}
options <- c("e4", "e5", "e6", "places", "people")
lapply(
  mapply(swli, type = options, paragraphs = 1),
  strwrap
)
```

## Quirks & Bugs
Due to the randomisation of paragraphs for return, the original JS auther
returns 5 paragraphs when a request for length 0 comes in.

The `window` scope in the original javascript errors when called by V8 so
the version locally has this replaced with `global`.
